---
title: "Documentation"
output: 
  md_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)

file <- here("R/misc.R")
file.exists(file)
```




## Scripts

```{r}
scripts <- list.files(here("R"))
scripts %>% writeLines
```


## Packages used

```{r}
pkgs <- map(scripts, ~readr::read_lines(here("R", .x)) %>% str_extract("[a-zA-Z_-]*(?=::)") %>% na.omit %>% as.character) %>% unlist %>% 
  unique %>% sort %>% .[-1]

pkgs %>% writeLines


```

## Functions

```{r}
fcts <- map(scripts, ~readr::read_lines(here("R", .x)) %>% str_extract("^.*(?= <- function\\()") %>% na.omit %>% as.character) %>% unlist %>% 
  .[str_detect(., "^[a-zA-Z]")]

fcts %>% writeLines

```


### Spatial analysis

extract_nearest  
extract_nearest_layer  
extract_nearest_value  
splibs  
make_grid


### Mapping

gp_pointmap  
gp_point_neighbor  
gp_open_gmaps  
gp_gplot


### ggplot helpers

one1_line  
plot_corr  
gp_ggaes


### Compare datasets

comp_sim_df  
comp_for  
comp_btw


### Flag entries in list-column

make_flag_col  
add_flag  
get_flag


### Misc

knit_w_tmst  
coldesc  
which.nonnum  
nonumdf  
gp_dputran  
gp_file_opened  
gp_jobinfo  
gp_scale2  
wrnam  
mk_hdr  
up_date  
paste_na  
gp_unwrap  
prinf


### Data archiving (archd_fct.R)

#### ArchD

This project is mostly deprecated. It provided a form of version control for dataset that were modified within and without R, with saving intermediate versions. It worked quite well, but was possibly overkill for most tasks. It was abandoned in favor of a simpler approach implemented with file tracking.

Functions: ad_init, ad_archive, ad_save, ad_to_date, ad_lsv, default_fold, mk_timestamp, same_file, create_log, update_log, comp_dfs, list_cols_to_csv


#### File tracking

saveme  
ggsaveme  
record_meta  
create_project_file_tracking  
tmst  
ptmst  
hptmst  
last_tmst  
list_tmst  


### Data Viz
plot_psem  
plot_lavaan  
psemtolav


```{r eval=FALSE, include=FALSE}

if (file.exists("documentation.md")) {

  fs::file_copy("documentation.md", "../README.md")
  
}

```

